Optimistic Atomic Multicast in One Communication Delay

### 2011-07-22 textos/optpaxos/draft_dropbox.tex
revising proofs

\begin{proof}
Consider Algorithm \ref{algorithm:deliveryminimal}. Whenever a process in a group $g$ \amcast{}s a message, it is first \rmcast{} to all processes in $g$ (l. \ref{algline:rmlocal}). From the properties of the \rmcast{} primitive, every correct process from $g$ \rmdel{}s $m$ and inserts it into its $\localmsgs$ set (l. \ref{algline:addtogroupmsgs}). From Lemma \ref{lemma:mcastdecided}, $m$ will eventually be decided within $g$. At this point, if $g \in m.dst$, every correct process of $g$ will also insert $m$ into its $\stamped$ set (l. \ref{algline:insbp2}). Besides, each correct process in $g$ \rmcast{}s $m$ to all other destination groups that $m$ is adressed to (l. \ref{algline:rmothers}).

>>>>

\begin{proof}
In Algorithm \ref{algorithm:deliveryminimal}, whenever a process in a group $g$ \amcast{}s a message, it is first \rmcast{} to all processes in $g$ (l. \ref{algline:rmlocal}). From the properties of the \rmcast{} primitive, every correct process from $g$ \rmdel{}s $m$ and inserts it into $\localmsgs$ (l. \ref{algline:addtogroupmsgs}). From Lemma \ref{lemma:mcastdecided}, $m$ will eventually be decided within $g$. When this happens, if $g \in m.dst$, every correct process of $g$ also inserts $m$ into $\stamped$ (l. \ref{algline:insbp2}). Besides, each correct process in $g$ \rmcast{}s $m$ to all other groups that $m$ is adressed to (l. \ref{algline:rmothers}).
